---
title: "Additional notes / Rough working"
author: "Benjamin Evans"
format: 
  html:
    includes:
      in-header: webexercises-deps.html
editor:
  markdown:
    wrap: 72
  render-on-save: true
jupyter: false
---

```{r setup}
#| echo: false
library(webexercises)
```

# Testing ?

::: {.challenge}
### Quick Quiz

Which of these is used to join datasets in R?

`r webexercises::mcq(c(answer = 'left_join()', 'merge()', 'rbind()', 'spread()'))`

:::

- What is 1 and this `r webexercises::mcq(c(answer = 'left_join()', 'merge()', 'rbind()', 'spread()'))`
- Is this true? Answer: `r webexercises::torf(TRUE)`
- Is this true? Answer: `r webexercises::torf(FALSE)`

```{r}
#| echo: false
opts_p <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)
```
Test your knowledge:
`r webexercises::longmcq(opts_p)`


::: {.webex-check .webex-box}

I am going to learn a lot: `r torf(TRUE)`

```{r, results='asis', echo = FALSE}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("What is a p-value?", longmcq(opts))
```

:::


`r hide("Click here to see the solution")`

```{r, echo = FALSE}
hist(rnorm(1000))
```

`r unhide()`

### Fill-In-The-Blanks (`fitb()`)

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

- 2 + 2 is `r fitb(4)`

::: {.callout-note}
This is a note callout.
:::

::: {.callout-warning}
This is a warning callout
:::

::: {.callout-important}
This is an important callout
:::

::: {.callout-caution}
This is a caution callout
:::

::: {.callout-tip}
This is a tip callout.With a bit of `code`.
:::